Near Optimal Behavior via Approximate State Abstraction

### 2016-02-05 paper/results_discussion.tex
prep for merge

\section{Approximate Abstraction on Example Domains}
%Explanation of what abstraction is used
We ran experiments on aggregation functions in the $\epQ$ family of approximate abstractions. We provide results for only $\epQ$ because, as our proofs in Section \ref{sec:theory_results} demonstrate, the other three functions are reducible to particular $\epQ$ functions. For the purpose of illustrating what kinds of approximations are possible, we built each abstraction by first solving the MDP, then greedily aggregating ground states into abstract states that satisfied the $\epQ$ criteria. Since this approach represents an order-dependent approximation to the maximum amount of abstraction possible, we randomized the order in which states were considered across trials. Every ground state is equally weighted in its abstract state.

@@

% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For NChain and Minefield.
\begin{figure*}
\centering
\subfigure[NChain]{
\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.pdf}
}
\subfigure[Minefield]{
\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.pdf}
}
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.pdf}
}
\subfigure[Random]{
\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_num_abstract_states.pdf}
}

>>>>

\section{Approximate Abstraction on Example Domains}

% Figure: Epsilon vs. #States and Epsilon vs Abstract Pol. For NChain and Minefield.
\begin{figure*}[t]
\centering
\subfigure[NChain]{
\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.pdf}
}
\subfigure[Minefield]{
\includegraphics[width=0.46\columnwidth]{figures/minefield_epsilon_vs_num_abstract_states.pdf}
}
\subfigure[Taxi]{
\includegraphics[width=0.46\columnwidth]{figures/taxi_epsilon_vs_num_abstract_states.pdf}
}
\subfigure[Random]{
\includegraphics[width=0.46\columnwidth]{figures/random_epsilon_vs_num_abstract_states.pdf}
}

%Explanation of what abstraction is used
We ran experiments with aggregation functions in the $\epQ$ family of approximate abstractions. We provide results for only $\epQ$ because, as our proofs in Section \ref{sec:theory_results} demonstrate, the other three functions are reducible to particular $\epQ$ functions. For the purpose of illustrating what kinds of approximations are possible we built each abstraction by first solving the MDP, then greedily aggregating ground states into abstract states that satisfied the $\epQ$ criteria. Since this approach represents an order-dependent approximation to the maximum amount of abstraction possible, we randomized the order in which states were considered across trials. Every ground state is equally weighted in its abstract state.

@@
